NGO analysis

### 2022-07-29 Dashboard/Dashboard filename tests.Rmd
More download testing.

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed and avoiding
# catastrophic dashboard errors if they're not available
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

## Download button -------------------------------------------------------------
output$downloadUI <- renderUI({
  downloadButton("report", "Download report")
})

## Report download and parameters ----------------------------------------------s
output$report <- downloadHandler(

  # Based on code in Mastering Shiny
  filename = "report.pdf",
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

    # R Markdown render
    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
```

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed and avoiding
# catastrophic dashboard errors if they're not available
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using the fontawesome package for more up-to-date (and currently supported)
# Fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())

# It's possible to hide the download button until conditions are satisfied, but
# is it really worth the effort?
```

@@

## Download button -------------------------------------------------------------

```

  output$downloadUI <- renderUI({
  downloadButton("report", "Download report")
})

  ## Report download and parameters ----------------------------------------------

  report_title <- reactive({
    str_c(title(), "_", Sys.Date(), ".pdf")
  })

  output$report <- downloadHandler(

  # Based on code in Mastering Shiny
  filename = report_title(),
  content = function(file) {
    tempReport <- file.path(tempdir(), "report.Rmd")
    file.copy("report.Rmd", tempReport, overwrite = TRUE)

@@

    # R Markdown render
    rmarkdown::render(tempReport,
      output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
